Questions to Developers

### 2021-06-24 StateOfPractice/Ao-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
Update to Ao presentation slides to make them more Ao specific

@@

\begin{frame}
\frametitle{Domain Analysis}

\bi
\item So users can pick the right software for their task
\item Think of the software as a family of related software products, like:
\bi
\item Family of automobiles
\item Computer hardware
\item ...
\ei
\item Commonalities
\item Variabilities
\item Parameters of variation
\item Do the following slides capture the commonalities and variabilities?
\item We can follow up over e-mail, if that is easier
\ei

\begin{frame}
\frametitle{Commonalities}

[Peter, please list your commonalities here; Ao, we'll use a scope slide
instead]

\begin{frame}
\frametitle{Variabilities}

[Peter, please list your variabilities, with their associated parameters of
variation here; Ao, you can delete this slide]

>>>>

\begin{frame}
\frametitle{Scope}

[Ao put your scope figure here.  Peter, you can delete this slide.]

@@
